### 2019-07-30 0_abstract.tex
Tweak abstract to make performance claims.

\begin{abstract}
% 148 words
We present Task Bench, a \emph{parameterized} benchmark designed to
explore the performance of parallel and distributed
programming systems under a variety of application scenarios. Task
Bench lowers the barrier to benchmarking multiple programming systems by making
the implementation for a given system orthogonal to the benchmarks
themselves: every benchmark constructed with Task Bench
runs on every Task Bench implementation. Furthermore,
Task Bench's parameterization allows a wide variety of benchmark
scenarios that distill the key characteristics of larger applications.

We conduct a comprehensive study with implementations of Task Bench in
15 programming systems on up to 256 Haswell nodes of the Cori
supercomputer. We introduce and use a novel metric, \emph{minimum effective task
  granularity} to study the baseline runtime overhead of each system
and the impact of different dependence patterns. We also
study each system's scalability, ability to hide communication and
mitigate load imbalance.
\end{abstract}

>>>>

\begin{abstract}
We present Task Bench, a \emph{parameterized} benchmark designed to
explore the performance of parallel and distributed
programming systems under a variety of application scenarios. Task
Bench lowers the barrier to benchmarking multiple programming systems by making
the implementation for a given system orthogonal to the benchmarks
themselves: every benchmark constructed with Task Bench
runs on every Task Bench implementation. Furthermore,
Task Bench's parameterization enables a wide variety of benchmark
scenarios that distill the key characteristics of larger applications.

We conduct a comprehensive study with implementations of Task Bench in
15 programming systems on up to 256 Haswell nodes of the Cori
supercomputer. We introduce a novel metric, \emph{minimum effective task
  granularity} to study the baseline runtime overhead of each
system. We show that when running at scale, 100~\textmu{}s is the
smallest granularity that even the most efficient systems can reliably
support with current technologies. We also study each system's
scalability, ability to hide communication and mitigate load
imbalance.
\end{abstract}

### 2019-07-30 1_introduction.tex
Tweak abstract to make performance claims.

We present Task Bench, a parameterized benchmark designed for exploring the performance
of parallel and distributed programming systems under a
variety of conditions.  The key property of Task Bench is that it completely separates
the system-specific implementation from the core implementation
of the benchmarks themselves.
In all benchmarks we know of, the effort to implement $n$ benchmarks on $m$
systems is $\mathcal{O}(mn)$.  Task Bench's design reduces this work to $\mathcal{O}(m + n)$,
enabling dramatically more systems and benchmarks to be explored for the same amount of programming
effort.  New benchmarks created with Task Bench
immediately run on all systems, and new systems that implement the Task Bench interface immediately run all
benchmarks.

Benchmarks in Task Bench are based on the observation that many applications can be modeled
as a set of \emph{tasks}, or coarse-grain units of work, with
dependencies between tasks representing the communication and synchronization required for
distributed execution. A benchmark consists of a \emph{task graph} with tasks for
each point in an \emph{iteration space}, and dependencies
determined by a \emph{dependence relation}. This design permits a
concise description of a wide variety of patterns relevant to
scientific computing and large scale data analysis: trivial parallelism, halo exchanges (such as
seen in structured and unstructured mesh codes), sweeps (such as used
in the discrete ordinates method of radiation simulation), FFTs, trees
(for divide and conquer algorithms), and so on. The tasks at each
point in the task graph can be configured to execute kernels with a
variety of computational properties, including compute- and
memory-bound operations of varying durations. The dependencies between
tasks can be configured to carry communication payloads of varying size, permitting
the design of communication-bound cases. Finally, multiple
(potentially heterogeneous) task graphs can be executed concurrently
to introduce task parallelism into the workload. Together, these
design elements permit the exploration of a large space of application
behaviors.

>>>>

We present Task Bench, a parameterized benchmark for exploring the performance
of parallel and distributed programming systems under a
variety of conditions.  The key property of Task Bench is that it completely separates
the system-specific implementation from the implementation
of the benchmarks themselves.
In all previous benchmarks we know of, the effort to implement $m$ benchmarks on $n$
systems is $\mathcal{O}(mn)$.  Task Bench's design reduces this work to $\mathcal{O}(m + n)$,
enabling dramatically more systems and benchmarks to be explored for the same amount of programming
effort.  New benchmarks created with Task Bench
immediately run on all systems, and new systems that implement the Task Bench interface immediately run all
benchmarks.

Benchmarks in Task Bench are based on the observation that many applications can be modeled
as a set of \emph{tasks}, or coarse-grain units of work, with
dependencies between tasks representing the communication and synchronization required for
distributed execution. A benchmark consists of a \emph{task graph} with tasks for
each point in an \emph{iteration space}, and dependencies
determined by a \emph{dependence relation}. This design permits a
concise description of a wide variety of patterns relevant to
scientific computing and large scale data analysis: trivial parallelism, halo exchanges (such as
seen in structured and unstructured mesh codes), sweeps (such as used
in the discrete ordinates method of radiation simulation), FFTs, trees
(for divide and conquer algorithms), and so on. Tasks execute kernels with a
variety of computational properties, including compute- and
memory-bound operations of varying durations. Dependencies between
tasks can be configured to carry communication payloads of varying size, permitting
the design of communication-bound cases. Finally, multiple
(potentially heterogeneous) task graphs can be executed concurrently
to introduce task parallelism into the workload. Together, these
design elements enable the exploration of a large space of application
behaviors.
